Dominance Regions for Rank Two Cluster Algebras

### 2022-04-09 dominance_regions.tex
opposite g-vectors
Preparing for the proof of Theorem 1.4

\newcommand{\cA}{\mathcal{A}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cQ}{\mathcal{Q}}
\newcommand{\cS}{\mathcal{S}}

@@

  When $bc\le3$, the cluster algebra $\cA(b,c)$ will be of finite-type and cluster monomials form its only pointed basis.
  We will therefore assume that $bc\ge4$.
  In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
  Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside its \emph{dominance polygon} $\cP(\lambda)$.
  %In this case, we compute the possible transitions between any two pointed bases.
  %The collection of $\bfg$-vectors which can appear in the deformation of a pointed basis is the \emph{dominance region}.
  \begin{theorem}
    \label{th:dominance inequalities}
    The dominance polygon $\cP(\lambda)$ pointed at $\lambda=(\lambda_0,\lambda_1)$ is the region consisting of those $\mu\in\RR^2$ satisfying $\mu_0 \leq \lambda_0, \mu_1 \geq\lambda_1$, and the following inequalities:
    {
      \everymath={\displaystyle}
      \def\arraystretch{2.8}
      \[
        \begin{array}{rcccl}
          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) & \leq & \max\left(-c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1,0\right)
          \\
          \min\left(-c\lambda_0,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) & \leq & 0
          \\
          0 & \leq &  -(\mu_0-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1,0\right)
          \\
          \min\left(b \lambda_1,0\right) & \leq & (\mu_0-\lambda_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda_1) & \leq & 0
        \end{array}
      \]
    }
  \end{theorem}

@@

  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
  \begin{corollary}
    \label{cor:dominance vertices}
    There are six classes of dominance polytopes.
    \begin{enumerate}
      \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cP(\lambda)$ is the point $\lambda$. 
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_0-b\lambda_1,c\lambda_0+2\lambda_1\big)$.
      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0\big)$, and $\big(0,\frac{\sqrt{bc(bc-4)}}{b}\ell\big)$.
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP(\lambda)$ is the kite with corner vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_0+b\lambda_1,c\lambda_0+2\lambda_1)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$.
      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0\big)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell\big)$.
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$.
    \end{enumerate}
  \end{corollary}

@@

  We begin by studying transformations of $\RR^2$ which determine the change of $\bfg$-vectors when expanding a pointed expression of the form~\eqref{eq:pointed} in terms of a cluster $\{x_k,x_{k+1}\}$.
  Write $\phi_0:\RR^2\to\RR^2$ for the identity map and define piecewise-linear maps $\phi_{\pm 1}:\RR^2\to\RR^2$ as follows:
  \begin{equation}
    \phi_1(\lambda)
    =
    \begin{cases} 
      (-\lambda_0,c\lambda_0+\lambda_1) & \text{if $\lambda_0 \ge 0$;}\\
      (-\lambda_0,\lambda_1) & \text{if $\lambda_0 < 0$;}
    \end{cases}
    \qquad
    \phi_{-1}(\lambda)
    =
    \begin{cases} 
      (\lambda_0,-\lambda_1) & \text{if $\lambda_1 \ge 0$;}\\
      (\lambda_0+b\lambda_1,-\lambda_1) & \text{if $\lambda_1 < 0$.}
    \end{cases}
  \end{equation}
  For $k\in\ZZ$ with $|k|>1$, define piecewise-linear maps
  \[\phi_k
    :=
    \begin{cases}
      (\phi_{-1}^{-1}\phi_1)^j & \text{if $k=2j$;}\\
      \phi_1(\phi_{-1}^{-1}\phi_1)^j & \text{if $k=2j+1$.}\\
    \end{cases}
  \]
  These determine the dominance region as follows.
  \begin{definition}
    \label{def:dominance}
    For $\lambda\in\ZZ^2$ and $k\in\ZZ$, define cones 
    \[\cC_k(\lambda)
      :=
      \begin{cases}
        \{(\lambda_0-r,\lambda_1+s):r,s\in\RR_{\ge0}\} & \text{if $k=2j$;}\\
        \{(\lambda_0+r,\lambda_1-s):r,s\in\RR_{\ge0}\} & \text{if $k=2j+1$.}
      \end{cases}
    \]
    The \emph{dominance region} $\cP(\lambda)$ is the intersection  $\bigcap_{k\in\ZZ}\phi_k^{-1}\cC_k(\phi_k\lambda)$.
    When $\mu\in\cP(\lambda)$, we say \emph{$\lambda$ dominates $\mu$}.
  \end{definition}

@@

  Here we explicitly compute the dominance regions $\cP(\lambda)$.
  When $\lambda$ is not imaginary, the dominance region is particularly simple.
  \begin{lemma}
    \label{le:cluster monomials}
    If $\lambda\in\ZZ^2\setminus\cI$, then $\cP(\lambda)=\{\lambda\}$.
  \end{lemma}
  \begin{proof}
    Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_k^{\alpha_k}x_{k+1}^{\alpha_{k+1}}$.
    In this case the intersection
    \[\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda) \cap \phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)\]
    is precisely $\{\lambda\}$. 
    Indeed, when $k$ is odd the cone $\cC_{k-1}(\phi_{k-1}\lambda)$ lies entirely within a domain of linearity for $\phi_{k-1}^{-1}$.
    In particular, $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda)$ is a cone containing $\lambda$ directed away from the origin (with walls parallel to the boundary of the domain of linearity containing $\lambda$).
    On the contrary, when $k$ is odd the cone $\cC_{k+1}(\phi_{k+1}\lambda)$ intersects the domain of linearity for $\phi_{k+1}^{-1}$ containing $\phi_{k+1}\lambda$ (resp. $\phi_{k-1}\lambda$) in a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\phi_{k+1}\lambda$ (resp. $\phi_{k-1}\lambda$).
    In particular, $\phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$ (resp. $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda)$) is a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\lambda$.
    The result follows.
  \end{proof}
  To compare with Theorem~\ref{th:dominance inequalities}, we consider three cases in which $\lambda\in\ZZ^2\setminus\cI$:
  \begin{itemize}
    \item if $\lambda_0 \le 0$ and $\lambda_1 \ge 0$, the second and fourth inequalities become equations for lines which intersect at $\lambda$;
    \item if $\lambda_0 > 0$ and $\lambda_1 \ge \frac{-bc+\sqrt{bc(bc-4)}}{2b}\lambda_0$, the first and second inequalities become equations for lines which intersect at $\lambda$;
    \item if $\lambda_1 < 0$ and $\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2c}\lambda_1$, the third and fourth inequalities become equations for lines which intersect at $\lambda$.
  \end{itemize}
  This proves Theorem~\ref{th:dominance inequalities} when $\lambda\notin\cI$.

  Next we aim to understand how inequalities transform under the action of a linear map, this will be the key tool for describing the dominance regions $\cP(\lambda)$ for $\lambda\in\cI$.

@@

  We are now ready to prove Theorem~\ref{th:dominance inequalities}.
  The dominance region $\cP(\lambda)=\bigcap_{k\in\ZZ}\phi_k^{-1}\cC_k(\phi_k\lambda)$ for $\lambda\in\cI$ is obtained by imposing all of the inequalities from Lemma~\ref{le:dominance inequalities} together with $\mu_0 -\lambda_0 \le 0$ and $0 \le \mu_1 - \lambda_1$ coming from $k=0$.

@@

  For $\mu_1-\lambda_1\ge 0$, the inequalities \eqref{ieq1} become more restrictive as $k$ gets larger since the sequence $\frac{-u_{k+1}^-}{u_k^+}$ of slopes is monotonically decreasing.
  Thus in the limit as $k\to\infty$, we obtain the inequality 
  \[ 0 \le \frac{-bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \]
  or equivalently
  \[ 0 \le -(\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \]
  determining a boundary of $\cP(\lambda)$.

  Similarly, the inequalities \eqref{ieq2} become more restrictive for $\mu_0\le0$ and $\mu_1\ge0$ as $k$ gets larger since the sequence of slopes $\frac{u_{k-1}^-}{u_k^+}$ is monotonically increasing and the intersection with \eqref{ieq1} moves lower on the $\mu_1$-axis as $k$ increases.
  Thus in the limit as $k\to\infty$, we obtain the inequality
  \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \]
  determining a boundary of $\cP(\lambda)$.
  Observe further that $\mu_0-\lambda_0 \le 0$ and $0 \le \mu_1-\lambda_1$ allow to strengthen this as
  \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \le 0. \]

  Finally, the inequalities \eqref{ieq3} become more restrictive for $\mu_1\le0$ as $k$ gets larger since the sequence of slopes $\frac{-u_{k-1}^+}{u_k^-}$ is monotonically increasing and the intersection with \eqref{ieq2} moves to the right on the $\mu_0$-axis as $k$ increases.
  Thus in the limit as $k\to\infty$, we obtain the inequality
  \[ -(\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \le \frac{bc+\sqrt{bc(bc-4)}}{2c}c\lambda_0+b\lambda_1 \]
  determining a boundary of $\cP(\lambda)$.

  Similar arguments with the inequalities \eqref{ieq4}-\eqref{ieq6} lead to the remaining inequalities determining the boundary of $\cP(\lambda)$:
  \[ 0 \le (\mu_0-\lambda_0)+\frac{bc+\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1);\]
  \[ b\lambda_1 \le (\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \le 0;\]
  \[ c\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2b}b\lambda_1 \le -\frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1).\]
  These can easily be seen to be equivalent to the remaining inequalities from Theorem~\ref{th:dominance inequalities} and this complete the proof.

@@

>>>>

\newcommand{\cA}{\mathcal{A}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cQ}{\mathcal{Q}}
\newcommand{\cS}{\mathcal{S}}

@@

  When $bc\le3$, the cluster algebra $\cA(b,c)$ will be of finite-type and cluster monomials form its only pointed basis.
  We will therefore assume that $bc\ge4$.
  In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
  Specifically, we show that the $\bfg$-vector $\lambda$ dominates the collection of $\bfg$-vectors of the form $\lambda+(b \alpha_0 ,c \alpha_1)$, $\alpha_0,\alpha_1\in\ZZ$, inside its \emph{dominance polygon} $\cP_\lambda$.
  \sayDR{Should we write $\cD_\lambda$ instead for "dominance"?}
  %In this case, we compute the possible transitions between any two pointed bases.
  %The collection of $\bfg$-vectors which can appear in the deformation of a pointed basis is the \emph{dominance region}.
  \begin{theorem}
    \label{th:dominance inequalities}
    The dominance polygon $\cP_\lambda$ pointed at $\lambda=(\lambda_0,\lambda_1)$ is the region consisting of those $\mu\in\RR^2$ satisfying $\mu_0 \leq \lambda_0, \mu_1 \geq\lambda_1$, and the following inequalities:
    {
      \everymath={\displaystyle}
      \def\arraystretch{2.8}
      \[
        \begin{array}{rcccl}
          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) & \leq & \max\left(-c\lambda_0-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_1,0\right)
          \\
          \min\left(-c\lambda_0,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) & \leq & 0
          \\
          0 & \leq &  -(\mu_0-\lambda_0)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda_1) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_0+b\lambda_1,0\right)
          \\
          \min\left(b \lambda_1,0\right) & \leq & (\mu_0-\lambda_0) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (\mu_1-\lambda_1) & \leq & 0
        \end{array}
      \]
    }
  \end{theorem}

@@

  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
  \begin{corollary}
    \label{cor:dominance vertices}
    There are six classes of dominance polytopes.
    \begin{enumerate}
      \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cP_\lambda$ is the point $\lambda$. 
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP_\lambda$ is the trapezoid with corner vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_0-b\lambda_1,c\lambda_0+2\lambda_1\big)$.
      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP_\lambda$ is the triangle with corner vertices $\lambda$, $\big(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0\big)$, and $\big(0,\frac{\sqrt{bc(bc-4)}}{b}\ell\big)$.
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP_\lambda$ is the kite with corner vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_0+b\lambda_1,c\lambda_0+2\lambda_1)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_0+\lambda_1\big)$.
      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP_\lambda$ is the triangle with corner vertices $\lambda$, $\big(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0\big)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell\big)$.
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP_\lambda$ is the trapezoid with corner vertices $\lambda$, $\big(\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_0+b\lambda_1,-c\lambda_0-(bc-2)\lambda_1\big)$.
    \end{enumerate}
  \end{corollary}

@@

  We begin by studying transformations of $\RR^2$ which determine the change of $\bfg$-vectors when expanding a pointed expression of the form~\eqref{eq:pointed} in terms of a cluster $\{x_k,x_{k+1}\}$.
  Write $\phi_0:\RR^2\to\RR^2$ for the identity map and define piecewise-linear maps $\phi_{\pm 1}:\RR^2\to\RR^2$ as follows:
  \begin{equation}
    \phi_1(\lambda)
    =
    \begin{cases} 
      (-\lambda_0,c\lambda_0+\lambda_1) & \text{if $\lambda_0 \ge 0$;}\\
      (-\lambda_0,\lambda_1) & \text{if $\lambda_0 < 0$;}
    \end{cases}
    \qquad
    \phi_{-1}(\lambda)
    =
    \begin{cases} 
      (\lambda_0,-\lambda_1) & \text{if $\lambda_1 \ge 0$;}\\
      (\lambda_0+b\lambda_1,-\lambda_1) & \text{if $\lambda_1 < 0$.}
    \end{cases}
  \end{equation}
  For $k\in\ZZ$ with $|k|>1$, define piecewise-linear maps
  \[\phi_k
    :=
    \begin{cases}
      (\phi_{-1}^{-1}\phi_1)^j & \text{if $k=2j$;}\\
      \phi_1(\phi_{-1}^{-1}\phi_1)^j & \text{if $k=2j+1$.}\\
    \end{cases}
  \]
  These determine the dominance region as follows.
  \begin{definition}
    \label{def:dominance}
    For $\lambda\in\ZZ^2$ and $k\in\ZZ$, define cones 
    \[\cC_k(\lambda)
      :=
      \begin{cases}
        \{(\lambda_0-r,\lambda_1+s):r,s\in\RR_{\ge0}\} & \text{if $k=2j$;}\\
        \{(\lambda_0+r,\lambda_1-s):r,s\in\RR_{\ge0}\} & \text{if $k=2j+1$.}
      \end{cases}
    \]
    The \emph{dominance region} $\cP_\lambda$ is the intersection  $\bigcap_{k\in\ZZ}\phi_k^{-1}\cC_k(\phi_k\lambda)$.
    When $\mu\in\cP_\lambda$, we say \emph{$\lambda$ dominates $\mu$}.
  \end{definition}

@@

  Here we explicitly compute the dominance regions $\cP_\lambda$.
  When $\lambda$ is not imaginary, the dominance region is particularly simple.
  \begin{lemma}
    \label{le:cluster monomials}
    If $\lambda\in\ZZ^2\setminus\cI$, then $\cP_\lambda=\{\lambda\}$.
  \end{lemma}
  \begin{proof}
    Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_k^{\alpha_k}x_{k+1}^{\alpha_{k+1}}$.
    In this case the intersection
    \[\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda) \cap \phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)\]
    is precisely $\{\lambda\}$. 
    Indeed, when $k$ is odd the cone $\cC_{k-1}(\phi_{k-1}\lambda)$ lies entirely within a domain of linearity for $\phi_{k-1}^{-1}$.
    In particular, $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda)$ is a cone containing $\lambda$ directed away from the origin (with walls parallel to the boundary of the domain of linearity containing $\lambda$).
    On the contrary, when $k$ is odd the cone $\cC_{k+1}(\phi_{k+1}\lambda)$ intersects the domain of linearity for $\phi_{k+1}^{-1}$ containing $\phi_{k+1}\lambda$ (resp. $\phi_{k-1}\lambda$) in a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\phi_{k+1}\lambda$ (resp. $\phi_{k-1}\lambda$).
    In particular, $\phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$ (resp. $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda)$) is a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\lambda$.
    The result follows.
  \end{proof}
  To compare with Theorem~\ref{th:dominance inequalities}, we consider three cases in which $\lambda\in\ZZ^2\setminus\cI$:
  \begin{itemize}
    \item if $\lambda_0 \le 0$ and $\lambda_1 \ge 0$, the second and fourth inequalities become equations for lines which intersect at $\lambda$;
    \item if $\lambda_0 > 0$ and $\lambda_1 \ge \frac{-bc+\sqrt{bc(bc-4)}}{2b}\lambda_0$, the first and second inequalities become equations for lines which intersect at $\lambda$;
    \item if $\lambda_1 < 0$ and $\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2c}\lambda_1$, the third and fourth inequalities become equations for lines which intersect at $\lambda$.
  \end{itemize}
  This proves Theorem~\ref{th:dominance inequalities} when $\lambda\notin\cI$.

  Next we aim to understand how inequalities transform under the action of a linear map, this will be the key tool for describing the dominance regions $\cP_\lambda$ for $\lambda\in\cI$.

@@

  We are now ready to prove Theorem~\ref{th:dominance inequalities}.
  The dominance region $\cP_\lambda=\bigcap_{k\in\ZZ}\phi_k^{-1}\cC_k(\phi_k\lambda)$ for $\lambda\in\cI$ is obtained by imposing all of the inequalities from Lemma~\ref{le:dominance inequalities} together with $\mu_0 -\lambda_0 \le 0$ and $0 \le \mu_1 - \lambda_1$ coming from $k=0$.

@@

  For $\mu_1-\lambda_1\ge 0$, the inequalities \eqref{ieq1} become more restrictive as $k$ gets larger since the sequence $\frac{-u_{k+1}^-}{u_k^+}$ of slopes is monotonically decreasing.
  Thus in the limit as $k\to\infty$, we obtain the inequality 
  \[ 0 \le \frac{-bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \]
  or equivalently
  \[ 0 \le -(\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \]
  determining a boundary of $\cP_\lambda$.

  Similarly, the inequalities \eqref{ieq2} become more restrictive for $\mu_0\le0$ and $\mu_1\ge0$ as $k$ gets larger since the sequence of slopes $\frac{u_{k-1}^-}{u_k^+}$ is monotonically increasing and the intersection with \eqref{ieq1} moves lower on the $\mu_1$-axis as $k$ increases.
  Thus in the limit as $k\to\infty$, we obtain the inequality
  \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \]
  determining a boundary of $\cP_\lambda$.
  Observe further that $\mu_0-\lambda_0 \le 0$ and $0 \le \mu_1-\lambda_1$ allow to strengthen this as
  \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \le 0. \]

  Finally, the inequalities \eqref{ieq3} become more restrictive for $\mu_1\le0$ as $k$ gets larger since the sequence of slopes $\frac{-u_{k-1}^+}{u_k^-}$ is monotonically increasing and the intersection with \eqref{ieq2} moves to the right on the $\mu_0$-axis as $k$ increases.
  Thus in the limit as $k\to\infty$, we obtain the inequality
  \[ -(\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \le \frac{bc+\sqrt{bc(bc-4)}}{2c}c\lambda_0+b\lambda_1 \]
  determining a boundary of $\cP_\lambda$.

  Similar arguments with the inequalities \eqref{ieq4}-\eqref{ieq6} lead to the remaining inequalities determining the boundary of $\cP_\lambda$:
  \[ 0 \le (\mu_0-\lambda_0)+\frac{bc+\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1);\]
  \[ b\lambda_1 \le (\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \le 0;\]
  \[ c\lambda_0+\frac{bc+\sqrt{bc(bc-4)}}{2b}b\lambda_1 \le -\frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1).\]
  These can easily be seen to be equivalent to the remaining inequalities from Theorem~\ref{th:dominance inequalities} and this complete the proof.

@@

  Every pointed basis element for $\cA(b,c)$ admits an opposite $\bfg$-vector arising by interchanging the roles of $b$, $c$ and $x_0$, $x_1$ in \eqref{eq:pointed}. 
  \begin{lemma}
    Given a $\bfg$-vector $\lambda$, the opposite $\bfg$-vector $\lambda'$ is obtained as follows:
    \begin{itemize}
      \item if $\lambda_0,\lambda_1\ge0$, then $\lambda'=\lambda$;
      \item if $\lambda_1\ge0$ and $\lambda_0<0$, then $\lambda'=(\lambda_0,-c\lambda_0+\lambda_1)$;
      \item if $\lambda_0>0$ and $\lambda_0+b\lambda_1>0$, then $\lambda'=(\lambda_0+b\lambda_1,\lambda_1)$;
      \item otherwise, $\lambda'=(\lambda_0+b\lambda_1,-c\lambda_0-(bc-1)\lambda_1)$.
    \end{itemize}
  \end{lemma}

  The support $\cG_\lambda$ of the greedy basis element of $\cA(b,c)$ with $\bfg$-vector $\lambda$ is well-known \cite{LLZ,cgmmrsw}.
  This is indicated by the solid and dashed lines in Theorem~\ref{th:maximum support} where dashed lines indicate points that are excluded from the support (note that the white dot does not indicate that this point is excluded).
  For our purposes, it is enough to observe the following closure property for the greedy support.
  \begin{definition}
    A subset $\cS\subset\RR^2$ is called \emph{DL-convex} if $\lambda,\mu\in\cS$ implies $\big(\min(\mu_0,\lambda_0),\min(\mu_1,\lambda_1)\big)\in\cS$.
  \end{definition}
  In particular, (an upper bound for) the greedy support can be found using the $\bfg$-vector indicated by a black dot and the opposite $\bfg$-vector indicated by a white dot in Theorem~\ref{th:maximum support}.
  Write $\overline{\cG}_\lambda$ for the cone of the DL-closure of $\{\lambda,\lambda'\}$, that is $\overline{\cG}_\lambda$ contains the segments joining $\lambda$ and $\lambda'$ with $\big(\min(\lambda_0,\lambda'_0),\min(\lambda_1,\lambda'_1)\big)$ and for any $\mu\in\overline{\cG}_\lambda$ we have $t\mu\in\overline{\cG}_\lambda$ for $0\le t\le 1$.
  Clearly, $\cG_\lambda\subset\overline{\cG}_\lambda$.
